Learning filters from user provided image makers

### 2020-06-07 main.tex
dataset description

\section{Experiments}
We use a dataset formed from patches of coconut images. The dataset consists of images of dimensions $90 \times 90$ of coconut and non-coconut. The latter class has a large variability. The problem of interest is to classify the images in one of the two classes.

@@

\begin{figure}
  \centering
  \subfloat[Visualization of original image feature space.]{\includegraphics[width=.45\linewidth]{figures/input}
  \label{fig:vis-input}}
  ~
  \subfloat[Visualization of the feature extractor's outputs.]{\includegraphics[width=.45\linewidth]{figures/feature_extractor}
  \label{fig:vis-feature-extractor}}
  \\
  \subfloat[Visualization of outputs from the last classifier hidden layer.]{\includegraphics[width=.45\linewidth]{figures/classifier}
  \label{fig:vis-classifier}}
  \caption{This image shows visualizations of the input images and the intermediate layer's outputs. Green points represent background images, and red points represent images that have a coconut tree. The projection from high dimensionality space to 2D was made using t-SNE. The original image shows much overlap between the classes; after applying the feature extractor with only one convolutional layer, we can see that the overlapping decreases considerably. Before the decision layer, the last layer put most of the images from one class on one side and the other on the other side.}
\end{figure}

>>>>

\section{Experiments}
We use a dataset formed from patches of aerial images made by \cite{8899005} from imagery provided by WeRobotics. The imagery with a resolution of 8cm was captured by the World Bank's UAVs for Disaster Resilience Program, collaborating with WeRobotics and OpenAerialMap in the Kindom of Tonga in October 2017. The Humanitarian OpenStreetMap community provided the annotation. The dataset consists of 13587 patches of dimensions $90 \times 90$ of coconut (10268) and non-coconut (3319). The latter class has a large variability. The problem of interest is to classify the images in one of the two classes.

@@

\begin{figure}
  \centering
  \subfloat[Visualization of original image feature space.]{\includegraphics[width=.45\linewidth]{figures/input}
  \label{fig:vis-input}}
  ~
  \subfloat[Visualization of the feature extractor's outputs.]{\includegraphics[width=.45\linewidth]{figures/feature_extractor}
  \label{fig:vis-feature-extractor}}
  \\
  \subfloat[Visualization of outputs from the last classifier hidden layer.]{\includegraphics[width=.45\linewidth]{figures/classifier}
  \label{fig:vis-classifier}}
  \caption{This image shows visualizations of the input images and the intermediate layer's outputs. Red points represent background images, and green points represent images that have a coconut tree. The projection from high dimensionality space to 2D was made using t-SNE. The original image shows much overlap between the classes; after applying the feature extractor with only one convolutional layer, we can see that the overlapping decreases considerably. Before the decision layer, the last layer put most of the images from one class on one side and the other on the other side.}
\end{figure}
